Mapping factors associated with adolescents' emotion dysregulation: A text-mining based systematic review

### 2020-06-09 manuscript.Rmd
Updates

author: 
  - name          : "Caspar J. van Lissa"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "Padualaan 14, 3584CH Utrecht, The Netherlands"
    email         : "c.j.vanlissa@uu.nl"

affiliation:
  - id            : "1"
    institution   : "Utrecht University faculty of Social and Behavioral Sciences, department of Methodology & Statistics"
  - id            : "2"
    institution   : "Open Science Community Utrecht"

authornote: |
  Caspar van Lissa, Department of Methodology and Statistics, Utrecht
  University, P.O. Box 80140, 3508 TC, Utrecht, The Netherlands. E-mail:
  C.vanLissa@uu.nl. This work is supported by a NWO Veni grant (NWO
  grant number VI.Veni.191G.090).

@@

The present paper aims to develop a nomological network of the constructs
related to adolescent emotion dysregulation, based on a systematic review of
the literature. A nomological network is a diagrammatic representation of a
phenomenon; a proto-theoretical device that describes relationships between
constructs relevant to the theory [see @alaviAligningTheoryMethodology2018;
@@cronbachConstructValidityPsychological1955;
@@mastersonNomologicalNetworkResearch2009]. It is a precursor to a more
explicit theory of the phenomenon. The present paper uses an inductive approach
to develop this nomological network. First, we conduct a systematic search to
elicit a corpus of relevant literature. Second, we use text mining techniques
to extract relevant constructs from the corpus. Third, we use a dictionary to
pare down the extracted constructs to meaningful superordinate categories.
Fourth, we map interrelations between these constructs. Fifth, we classify
contstructs as potential predictors or outcomes, and we categorize predictors
by level of analysis<!-- (CJ: Sameroff, which level of biopsychosocial)-->.
<!-- t, using text mining to map potential predictors of adolescent emotion
dysregulation.
identify relevant constructs of adolescents’ emotion regulation development,
and moderators of parents’ role therein. The resulting insights are
consolidated into theory.
The present study intends to map the extant literature
First, I will systematically review predictors currently considered relevant in
the adolescent emotion regulation literature.  -->

@@

lo <- matrix(c("start", "dedup", "rayyan", "asreview", "included",
               "", "dedup2", "excluded", "", ""), nrow = 5, ncol = 2)
nodes <- data.frame(
  name = c("start", "dedup", "dedup2", "rayyan", "asreview", "included", "excluded"), 
  label = c(
    paste0("Records identified through\nWeb of Science (n = ", nrow(recs), ")"), 
    paste0("Records after duplicates removed\n(n = ", nrow(unique_recs), ")"), 
    paste0("Duplicates removed\n(n = ", nrow(recs)-nrow(screen), ")"), 
    paste0("Articles screened for eligibility\nusing Rayyan (n = ", nrow(screen), ")"), 
    paste0("Articles screened for eligibility\nusing ASReview (n = ", nrow(screen), ")"), 
    paste0("Studies included in\nqualitative synthesis (n = ", nrow(recs_final), ")"),
    paste0("Excluded studies (n = ", nrow(screen)-nrow(recs_final), ")"))
)
edges <- data.frame(
  from = c("start", "dedup", "rayyan", "asreview",
           "dedup", "rayyan", "rayyan", "asreview"),
  to = c("dedup", "rayyan", "asreview", "included",
         "dedup2", "dedup2", "excluded", "excluded"),
  label = c("",   "", sum(screen$rayyan == "True"), "",
            paste0("n = ", sum(dups)), 
            paste0("n = ", rayyan_dups),
            paste0("n = ", sum(screen$rayyan == "False")),
            paste0("n = ", sum(screen$included == 1, na.rm = TRUE)-sum(screen$rayyan == "False"))
  )
)
p <- graph_sem(layout = lo, nodes = nodes, edges = edges, angle = 1, rect_height = 1.2, rect_width = 1.3)
ggsave("prismachart.png", p, device = "png")
ggsave("prismachart.svg", p, device = "svg")
knitr::include_graphics("prismachart.svg")
```

@@

For this first analysis, we relied on author-provided keywords.
We extracted keywords by document, and used a dictionary approach
to classify closely related terms.
The dictionary was created specifically for this study.
The lead author composed a first draft of the dictionary based on prior knowledge of the field.
This draft was subsequently updated in two ways:
First, while writing the introduction for this paper, key terms from the theoretical and empirical literature were added to the dictionary.
Second, by including commonly occurring uncategorized words during preliminary analyses of the data.
An exclusion list of methodological terms and other non-substantive words was generated using the same procedure.

>>>>

author: 
  - name          : "Caspar J. van Lissa"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Padualaan 14, 3584CH Utrecht, The Netherlands"
    email         : "c.j.vanlissa@uu.nl"

affiliation:
  - id            : "1"
    institution   : "Utrecht University faculty of Social and Behavioral Sciences, department of Methodology & Statistics"

authornote: |
  This work is supported by a NWO Veni grant (NWO
  grant number VI.Veni.191G.090). Acknowledgement: Lukas Beinhauer contributed
  substantially to the screening of articles.

@@

The present paper aims to develop a nomological network of the constructs
related to adolescent emotion dysregulation, based on a systematic review of
the literature. A nomological network is a diagrammatic representation of a
phenomenon; a proto-theoretical device that describes relationships between
constructs relevant to the theory [see @alaviAligningTheoryMethodology2018]. It is a precursor to a more
explicit theory of the phenomenon. The present paper uses an inductive approach
to develop this nomological network. First, we conduct a systematic search to
elicit a corpus of relevant literature. Second, we use text mining techniques
to extract relevant constructs from the corpus. Third, we use a dictionary to
pare down the extracted constructs to meaningful superordinate categories.
Fourth, we map interrelations between these constructs. Fifth, we classify
contstructs as potential predictors or outcomes, and we categorize predictors
by level of analysis<!-- (CJ: Sameroff, which level of biopsychosocial)-->.
<!-- t, using text mining to map potential predictors of adolescent emotion
dysregulation.
identify relevant constructs of adolescents’ emotion regulation development,
and moderators of parents’ role therein. The resulting insights are
consolidated into theory.
The present study intends to map the extant literature
First, I will systematically review predictors currently considered relevant in
the adolescent emotion regulation literature.  -->

@@

lo <- matrix(c("start", "dedup", "rayyan", "asreview", "included",
               "", "dedup2", "excluded", "", ""), nrow = 5, ncol = 2)

nodes <- data.frame(
  name = c("start", "dedup", "dedup2", "rayyan", "asreview", "included", "excluded"), 
  label = c(
    paste0("Records identified through\nWeb of Science (n = ", nrow(recs), ")"), 
    paste0("After duplicates removed\n(n = ", nrow(unique_recs), ")"), 
    paste0("Duplicates\n(n = ", nrow(recs)-nrow(screen), ")"), 
    paste0("Articles screened for eligibility\nusing Rayyan (n = ", nrow(screen), ")"), 
    paste0("Articles screened for eligibility\nusing ASReview (n = ", nrow(screen), ")"), 
    paste0("Studies included in\nqualitative synthesis (n = ", nrow(recs_final), ")"),
    paste0("Excluded studies (n = ", nrow(screen)-nrow(recs_final), ")"))
)

edges <- data.frame(
  from = c("start", "dedup", "rayyan", "asreview",
           "start", "rayyan", "rayyan", "asreview"),
  to = c("dedup", "rayyan", "asreview", "included",
         "dedup2", "dedup2", "excluded", "excluded"),
  label = c("",   "", paste0("n = ", sum(screen$rayyan == "True")), paste0("n = ", sum(screen$included == 0, na.rm = TRUE)-sum(screen$rayyan == "True")),
            paste0("n = ", sum(dups)), 
            paste0("n = ", rayyan_dups),
            paste0("n = ", sum(screen$rayyan == "False")),
            paste0("n = ", sum(screen$included == 1, na.rm = TRUE)-sum(screen$rayyan == "False"))
  )
)

p <- graph_sem(layout = lo, nodes = nodes, edges = edges, angle = 1, rect_height = 1.2, rect_width = 1.3)
ggsave("prismachart.png", p, device = "png")
ggsave("prismachart.svg", p, device = "svg")
knitr::include_graphics("prismachart.png")
```

## Corpus description

```{r, eval = FALSE}
# Plot papers per year
df_plot <- as.data.frame(table(recs_final$PY), stringsAsFactors = FALSE)
df_plot$Year = as.numeric(df_plot$Var1)
ggplot(df_plot, aes(x= Year, y= Freq))+geom_point() + geom_path(group =1)+
  theme_bw() + scale_y_log10()
```

@@

The corpus for this first analysis consisted of the author-provided keywords for the selected articles.
We extracted keywords by document, and used a dictionary approach
to classify related terms.
The dictionary was created specifically for this study.
The lead author composed a first draft of the dictionary based on prior knowledge of the field.
This draft was subsequently updated in two ways:
First, while writing the introduction for this paper, key terms from the theoretical and empirical literature were added to the dictionary.
Second, by including commonly occurring uncategorized words during preliminary analyses of the data.
An exclusion list of methodological terms and other non-substantive words was generated using the same procedure.

## Structural topic modeling

```{r}
if(run_everything) source("LDA_analysis.R")
```
To assess the homogeneity of the corpus, we conducted topic modeling using latent dirichlet allocation [@bleiLatentDirichletAllocation2003]. 
A range of 2-20 topics was considered.
Fit was evaluated based on the BIC, and interpretability was evaluated on the entropy of the posterior probabilities of documents to be assigned to the different topics.
The BICs followed a near-perfect linearly increasing trend, indicating that no subcorpora could be identified.
Congruently, all entropies were near-zero, which means that the posterior probabilities of documents to be assigned to the different topics were uniformly distributed.
Thus, no interpretable subcorpora could be identified, and we proceed with an analysis of the whole sample. <!-- Probably because each set of keywords has only a few indicators. -->
